Dependent Object Types

### 2012-09-22 doc/fool/article.tex
blurb about preservation not holding

Note that expansions do not always exist. %TODO

@@

>>>>

Note that expansions do not always exist; see
section~\ref{narrowing_exp} for illustration.

@@

Most of these counterexamples are related to narrowing, the phenomenon
that a type can become more precise after substitution: if a method
takes a parameter $x$ of type $U$, then when it is invoked, any
argument $v$ of type $S \sub U$ can be substituted -- this is the
narrowing effect: it is as if the context was changed from $x : U$ to
$x : S$. Sections~\ref{term_mem},~\ref{narrowing_exp}~and~\ref{narrowing_wf} each
present a counterexample related to narrowing.

The last counterexample, presented in section~\ref{patheq},
illustrates the need to relate path-dependent types after
reduction. This need for path-equality provisions in order for
preservation to hold is well-known from other calculi such as
Tribe~\cite{tribe} with path-dependent types and a small-step
operational semantics.

More generally, these counterexamples illustrate that preservation
doesn't hold because a term that typechecks can step to a term that
does not typecheck. However, these counterexamples to preservation are
not counterexamples to type-safety: i.e. these programs don't get
stuck -- they eventually step to a value.
